\documentclass[10pt,colorlinks,linkcolor=true,urlcolor=gray]{moderncv}

\moderncvtheme[blue, modroman]{classic}
\usepackage{cv_kleinschmidt}

\addbibresource{kleinschmidt.bib}

\name{Dave F.}{Kleinschmidt}
\email{dave.f.kleinschmidt@gmail.com}
\homepage{davekleinschmidt.com}
\social[github]{kleinschmidt}
\social[twitter]{@kleinschmidt}

\begin{document}

\makecvtitle

\section{Education}
\label{sec:education}

\cventry{2016}{Ph.D. Brain and Cognitive Sciences}{University of Rochester}{Rochester, NY}{}{\emph{Perception in a Variable but Structured World: The Case of Speech Perception}. Committee: T. Florian Jaeger (advisor), Richard Aslin, Lori Holt, Jeffrey Runner (chair)}
\cventry{2009}{B.A. Mathematics, concentration Cognitive Science}{Williams College}{Williamstown, MA}{\emph{Summa cum laude}, highest honors in Cognitive Science}{Senior thesis advisor: Safa Zaki}

\section{Appointments}
\label{sec:experience}

\cventry{2018}{Assistant Professor of Psychology and Center for Cognitive Science}{Rutgers University, New Brunswick}{}{}{}
\cventry{2016--2018}{C.V. Starr Fellow}{Princeton Neuroscience Institute}{}{}{}
\cventry{2009--2010}{Baggett Fellow}{University of Maryland, Linguistics Department}{}{}{Post-baccalaureate research fellowship. Advised by Bill Idsardi.}
\cventry{2006--2009}{Research Assistant}{Williams College, Department of Psychology}{}{}{Supervised by Safa Zaki.}

\section{Publications}
\label{sec:publications}

\footnotetext{* Indicates equal contributions.}

\nocite{*}
\printbibliography[heading=subbibliography,title={Papers},type=article, check=inpress]
\printbibliography[heading=subbibliography,heading=none,type=article, check=nopubstate]

\printbibliography[heading=subbibliography,title={Submitted and in preparation},
                   nottype=inproceedings, check=inprepsubmitted]

\printbibliography[heading=subbibliography,title={Refereed Proceedings Papers},type=inbook]

\printbibliography[heading=subbibliography,title={Presentations},
                   type=unpublished, check=notinprepsubmitted]

\section{Invited Talks}

\subsection{Colloquia}

\cventry{2020}{Cognitive, Auditory, and Neural Bases of Language and Speech
  (CANBLS)}{Duke (Institute for Brain Sciences)}{Nov 9, 2020}{}{}
\cventry{2019}{Integrated Language Science and Technology Seminar}{University of
  Pennsylvania}{October 25, 2019}{}{}
\cventry{}{Cognition and Language Workshop}{Stanford University}{May 9, 2019}{}{}
\cventry{}{Cognitive Science Center Colloquium}{Williams College}{April 11, 2019}{}{}
\cventry{2018}{Cognitive Brown Bag series}{Villanova University}{February 8, 2018}{}{}
\cventry{2017}{Psychology Dept. Perception/Action/Cognition seminar}{University of Connecticut}{October 30, 2017}{}{}
\cventry{2014}{New Zealand Institute of Language, Brain, and Behavior Seminar}{University of Canterbury}{December 9, 2014}{}{}
\cventry{}{Cognition and Language Workshop}{Stanford University}{October 2, 2014}{}{}
\cventry{}{Psychology Department Seminar}{Carnegie Melon University}{July 22, 2014}{}{}
\cventry{}{Language Processing Brown Bag Seminar}{Beckman Institute, University of Illinois}{March 6, 2014}{}{}
\cventry{}{Cognitive Science Colloquium}{Tufts University}{February 13, 2014}{}{}

\subsection{Conferences}

\cventry{2019}{Exploring the interface between linguistic processing and talker
  recognition}{Special session of the Annual Meeting of the Acoustical Society
  of America}{May 13, 2019}{}{}

\subsection{Internal}

\cventry{2019}{Rutgers Center for Cognitive Science Colloquium}{Rutgers, New
  Brunswick}{April 23, 2019}{}{}

\section{Teaching}
\label{sec:teaching}

\subsection{Rutgers University}

% todo: number of students?
\cventry{2020-F}{Psycholinguistics (graduate)}{Rutgers New Brunswick}{Psychology}{}{}
\cventry{2020-S}{Sensation and Perception}{Rutgers New Brunswick}{Psychology}{}{}
\cventry{2019-F}{Language and Cognition}{Rutgers New Brunswick}{Rutgers Center for
  Cognitive Science}{}{}
\cventry{2019-S}{Sensation and Perception}{Rutgers New Brunswick}{Psychology}{}{}
\cventry{2018-F}{Advanced Topics II ``Perception in a variable world''}{Rutgers
  New Brunswick}{Rutgers Center for Cognitive Science}{}{}

\subsection{University of Rochester}

\cventry{2013}{Teaching assistant: Foundations of Cognitive Science}{University of Rochester}{}{}{}
\cventry{2011--2012}{Teaching assistant: Cognition}{University of Rochester}{}{}{}

\subsection{Williams College}

\cventry{2009}{Teaching assistant: Ergodic Theory}{Williams College}{}{}{}

\section{Mentoring}

\subsection{PhD supervision}

\cvline{2018-\emph{present}}{Sten Knutsen, Psychology (primary advisor).}
\cvline{2018}{Gwendolyn Rehrig, Psychology (committee member).}

\subsection{PhD (external)}

\cvline{2020-\emph{present}}{Sahil Luthra, University of Connecticut, Department
  of Psychological Sciences}

\subsection{Masters supervision}

\cvline{\emph{in progress}}{Sten Knutsen, Psychology (primary advisor).}
\cvline{2019}{Yarkın Ergin, Rutgers Psychology (committee member).}
\cvline{2019}{Joseph Sommer, Rutgers Psychology (committee member).}

\subsection{Undergraduate supervision}
\cvline{2012}{Supervised three University of Rochester undergraduate independent
  study students (jointly with one other graduate student).}

\section{Grants}

\cvlistitem{\textbf{NIH F31 Ruth L. Kirschstein National Research Service Award (NRSA) Individual Predoctoral Fellowship}, 2015--2016.}
\cvlistitem {\textbf{National Science Foundation, Graduate Research Fellowship}, 2010--2014.}

\section{Honors and Awards}
\label{sec:honors-awards}

\cvlistitem{\textbf{Outstanding Dissertation Award (Natural Sciences)}, University of Rochester, 2017}
\cvlistitem{\textbf{Glushko Prize for Outstanding Doctoral Dissertations/theses in Cognitive Science}, Cognitive Science Society, 2017}
\cvlistitem{\textbf{Highest rated student abstract}, 2016 Meeting of the Society for the Neurobiology of Language}
\cvlistitem {\textbf{Best student presentation}, 2013 LSA Summer Institute Workshop: ``How the brain accommodates variability in linguistic representations''.}
\cvlistitem {\textbf{Best student talk}, 2011 Architectures and Mechanisms of Language Processing (AMLaP) Conference.}
\cvlistitem{\textbf{Sproull Fellowship}, University of Rochester, 2010--2015.}
\cvlistitem{\textbf{Baggett Fellowship}, University of Maryland Linguistics Department post-bac.~research fellowship, 2009--2010.}
\cvlistitem{Member, \textbf{Phi Beta Kappa} honors society, inducted 2008.}
\cvlistitem{\textbf{Dean's List}, Williams College, 2005--2009.}
\cvlistitem{\textbf{Tyng Scholarship}, Williams College, 2005--2009.}
\cvlistitem{\textbf{National Merit Scholar}, 2005.}
\cvlistitem{Maine Educational Association \textbf{Clyde Russel Scholarship}, 2005.}

\section{Service}
\label{sec:service}

\subsection{Department service}

\cvline{2020-\emph{present}}{Psychology department website committee}

\cvline{2018-\emph{present}}{Psychology department undergraduate honors
  committee}

\cvline{2018-\emph{present}}{Psychology department statistics committee}

\subsection{Statistics outreach}
\cvline{}{I work to advance statistical literacy among cognitive scientists,
  psychologists, and linguists, via presentations at workshops and tutorials on
  statistical methods.}
\cvline{2020}{\emph{\href{https://repsychling.github.io/tutorial.html}{Mixed
      Models in the Julia Programming Language}}, workshop at the Zentrum
  f\"ur interdisziplin\"are Forschung (Center for Interdisiciplinary Research),
  Universit\"at Bielefeld, Germany, co-organized with Reinhold Kliegl, Doug
  Bates, and Philip Alday}.
\cvline{2016--2018}{Weekly statistics workshops for Princeton Neuroscience
  Institute graduate students and postdocs (jointly with Mike Shvartsman)}
\cvline{2014}{Tutorial on simulation-based methods for understanding mixed models. \emph{SST 2014 Tutorial: Regression and mixed effects models}}
\cvline{2013}{Co-organized UR BCS Department statistics and data analysis working group with Steve Piantadosi.}
\cvline{2011}{\emph{Preparing data for analysis using R}, presentation with Alex B. Fine at University of Rochester BCS workshop on mixed-effects regression analysis for cognitive scientists.}
\cvline{2010}{\emph{ANOVA and Mixed-Effects Models in R for Language
    Scientists}, presentation at University of Maryland Linguistics Dept. Winter
  Storm language sciences workshop.}

\subsection{Open source software}

\cvline{}{I've contributed to a number of open source software projects.  I've made substantial contributions to:}

\cvlistitem{\textbf{\href{https://github.com/JuliaStats/StatsModels.jl}{StatsModels.jl}}:
  Primary maintainer and developer of StatsModels.jl, the statistical modeling
  package for the \href{http://julialang.org/}{Julia language}, which provides a
  familiar ``formula language'' for specifying regression models, contrast
  coding for categorical variables, etc.}
\cvlistitem{\textbf{\href{https://github.com/JuliaStats/MixedModels.jl}{MixedModels.jl}}:
  Mixed-effects regression in Julia.}
\cvlistitem{\textbf{\href{https://github.com/dcjones/Gadfly.jl}{Gadfly.jl}}:
  Data visualization in Julia, based on the grammar of graphics.}

\cvline{}{And contributed minor bug fixes and improvements to many JuliaStats
  packages as well as
  \textbf{\href{https://github.com/mpastell/Weave.jl}{Weave.jl}} (knitr-like
  functionality for Julia),
  \textbf{\href{https://github.com/ftilmann/latexdiff/}{latexdiff}},
  \textbf{\href{https://github.com/mroth/lolcommits}{lolcommits}}, a node.js
  \textbf{\href{https://github.com/jefftimesten/mturk}{mturk API}}, and
  \textbf{\href{https://github.com/JoFrhwld/FAAV}{FAAV/FAVE}}.}

\subsection{Reviewing}

\cvline{}{Ad hoc reivewer for
  \emph{Acta Psychologica};
  \emph{Annual Meeting of the Cognitive Science Society};
  \emph{Attention, Perception, \& Psychophysics};
  \emph{Cognition};
  \emph{Experimental Brain Research};
  \emph{Journal of the Acoustical Society of America};
  \emph{Journal of Experimental Psychology};
  \emph{Journal of Laboratory Phonology};
  \emph{Journal of Memory \& Language};
  \emph{Journal of Speech, Language, and Hearing Research};
  \emph{Language};
  \emph{Language and Cognitive Processes};
  \emph{Language Learning};
  \emph{MIT Press};
  \emph{NSF SBE};
  \emph{PLoS One};
  \emph{Psychonomic Bulletin and Review}; and
  \emph{Topics in Cognitive Science}
}

\end{document}


