\documentclass[11pt]{article}

\usepackage{times}

\usepackage[margin=1in]{geometry}

\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\usepackage{enumitem}
\setlist{nosep}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

% use (a) etc. for sections
\renewcommand{\thesection}{(\alph{section})}

\usepackage[compact]{titlesec}
\titleformat*{\section}{\large\bfseries}

\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[sorting=ydnt,style=apa,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{kleinschmidt.bib}

% clean up mendeley crap:
\AtEveryBibitem{\clearfield{month}}
\AtEveryBibitem{\clearfield{labelmonth}}

% make every occurrence of one author appear in boldface.
% http://tex.stackexchange.com/questions/33330/
% (modified to work with apa style by replacing "author" with "apaauthor"
\newcommand{\makeauthorbold}[1]{%
  \DeclareNameFormat{apaauthor}{%
    \ifthenelse{\value{listcount}=1}
    {%
      {\expandafter\ifstrequal\expandafter{\namepartfamily}{#1}{\mkbibbold{\namepartfamily\addcomma\addspace \namepartgiveni}}{\namepartfamily\addcomma\addspace \namepartgiveni}}
      %
    }{\ifnumless{\value{listcount}}{\value{liststop}}
        {\expandafter\ifstrequal\expandafter{\namepartfamily}{#1}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}
        {\expandafter\ifstrequal\expandafter{\namepartfamily}{#1}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}%
      }
    \ifthenelse{\value{listcount}<\value{liststop}}
    {\addcomma\space}
  }
}
\makeauthorbold{Kleinschmidt}

% don't print "retrieved from" for URLs
\DefineBibliographyStrings{american}{%
  retrieved = {},
  from = {}
}





\begin{document}

{\Large\bfseries Dr. David F. Kleinschmidt}\\
Assistant Professor\\
152 Frelinghuysen Ave, Piscataway, NJ\\
\href{mailto:dave.kleinschmidt@rutgers.edu}{dave.kleinschmidt@rutgers.edu}\\
\url{https://www.davekleinschmidt.com}

\vspace{0.5\baselineskip}
\hrule

\section{Professional Preparation}

Williams College, Williamstown, MA. Mathematics (concentration: Cognitive
Science).  BA \emph{summa cum laude} 2009.

University of Rochester, Rochester, NY. Brain and Cognitive Sciences. PhD, 2016.

Princeton University, Princeton, NJ. Computational cognitive neuroscience
(Princeton Neuroscience Institute: Cohen/Norman labs). 2016--2018.


\section{Appointments}

2018--present: Assistant Professor of Psychology and Cognitive Science,
  Rutgers, New Brunswick

\section{Products}

\begin{enumerate}
  \item \fullcite{Kleinschmidt2015}
  \item \fullcite{Kleinschmidt2016}
  \item \fullcite{Kleinschmidt2018}
  \item \fullcite{Kleinschmidt2019}
  \item \fullcite{Pajak2016}
  \item \fullcite{Kleinschmidt2018c}
  \item \fullcite{Kleinschmidt2016a}
  \item \fullcite{Kleinschmidt2015a}
  \item \fullcite{Salverda2014}
  \item \fullcite{Kleinschmidt2012b}
\end{enumerate}  

\section{Synergistic Activities}

\textbf{Open source software for data science:} Maintainer of a number of
open-source software packages for data science in the Julia language (in the
\href{https://github.com/JuliaData/}{JuliaData} and
\href{https://github.com/JuliaStats}{JuliaStats} organizations).  Special focus
on \href{https://github.com/JuliaStats/StatsModels.jl}{StatsModels.jl} which
provides expressive, performant tools for users to convert data from
spreadsheet-like ``tabular'' format to numeric arrays required for statistical
modeling.  These tools are directly depended on by 25 other packages (including
the widely used GLM.jl and MixedModels.jl), and indirectly by 79+ others.

\textbf{Data science outreach:} Instructor for data science and statistics
workshops for graduate and undergraduate students (2010--present).  Topics
include using version control and notebooks for reproducible research,
understanding fundamental statistical concepts (power, type I/II errors,
reproducibility, multiple comparisons, p values), multilevel regression,
Bayesian inference, etc.

\textbf{Open source data and software for phonetic science:} Released R packages
with research code
(\href{https://github.com/kleinschmidt/beliefupdatr}{beliefupdatr}, for
Kleinschmidt and Jaeger, 2015; and
\href{https://github.com/kleinschmidt/phondisttools}{phondisttools}, for
Kleinschmidt, 2019) and datasets (both collected and curated/packaged from other
sources).  These have been used in teaching undergraduate and graduate courses
and for published/in-press research at at least two other universities.

\textbf{Interdisciplinary teaching:} Designed and implemented a new ``Advanced
Topics'' senior seminar for undergraduate students in the Rutgers Center for
Cognitive Science (RuCCS).  Covered primary literature for topics ranging from
psychophysics of visual and language processing in humans to perceptual
neuroscience in non-human animals to computational studies of natural scene
statistics.  Developed new syllabus and \emph{active learning format} for the
RuCCS ``Language and Cognition'' 300-level course, using inquiry-based
exploration of primary literature and covering language universals, language
variation, language learning, language change, and linguistic relativity.

\textbf{Ad hoc reviewer} for NSF (SBE) proposals and
  \emph{Acta Psychologica};
  \emph{Annual Meeting of the Cognitive Science Society} (refereed proceedings);
  \emph{Attention, Perception, \& Psychophysics};
  \emph{Cognition};
  \emph{Journal of the Acoustical Society of America};
  \emph{Journal of Cognitive Neuroscience};
  \emph{Journal of Experimental Psychology};
  \emph{Journal of Laboratory Phonology};
  \emph{Journal of Memory \& Language};
  \emph{Journal of Speech, Language, and Hearing Research};
  \emph{Language};
  \emph{Language and Cognitive Processes};
  \emph{Language Learning};
  \emph{MIT Press};
  \emph{NSF SBE};
  \emph{PLoS One};
  \emph{Psychonomic Bulletin and Review}; and
  \emph{Topics in Cognitive Science}

\end{document}